Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-01-23 Report/appendix_tightness.tex
manosha

Since the allocated rate of user \me{j} is less than the queued packets, we can find a precoder \me{\mvec{m}{j}} with the additional power of \me{\Delta P} as \me{\mvec{m}{j}^\prime = \bar{\mbf{m}}_{j} + \mvec{V}{j} \mbf{e}^\prime}. Note that the new precoder has no impact on the interference constraint of other users. The newly found precoder \me{\mvec{m}{j}^\prime} minimize the queue of user \me{j} without affecting other user rates, there by reduces the objective further. It is in contradiction to our original assumption that the power is utilized for the user \me{i} making the constraints loose. It can be seen that the constraints are tight as long as there is one user with unserviced backlogged packets at each \ac{BS} with the given power budget. Since the objective is not to minimize the power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to minimize the current backlogged packets in the system.

>>>>

Since the allocated rate of user \me{j} is less than the queued packets, we can find a precoder \me{\mvec{m}{j}} with the additional power of \me{\Delta P} as \me{\mvec{m}{j}^\prime = \bar{\mbf{m}}_{j} + \mvec{V}{j} \mbf{e}^\prime}. Note that the new precoder has no impact on the interference constraint of other users. The newly found precoder \me{\mvec{m}{j}^\prime} minimize the queue of user \me{j} without affecting the rates of other user, there by reduces the objective further. It is in contradiction to our original assumption that the precoders are optimal and the objective is minimum. It can be seen that the constraints are tight as long as there is one user with unserviced backlogged packets at each \ac{BS} with the given power budget. Since the objective is not to minimize the power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to minimize the current backlogged packets in the system.

### 2015-01-23 Report/convergence_centralized.tex
manosha

Let us write the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{rCl} \label{con}
\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj} \\
\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
\end{IEEEeqnarray}
wher \me{g_2,f} are convex functions and \me{h} is a linear function. Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both. Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} corresponds to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}. Other convex constraints are addressed by the constraint \eqref{con-cvx}. With this, the feasible set of the problem \eqref{con} is given by 
\begin{IEEEeqnarray}{rl}
\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \nonumber
\end{IEEEeqnarray}

Before proceeding further, let us define the following notations. Let \me{\iterate{\mx}{k}} denote the \me{\ith{k}} \ac{BCDM} operating point and \me{\mx_k} represent the \me{\ith{k}} \ac{SCA} approximation point. Since the problem \eqref{con} is nonconvex, it is not guaranteed to find the optimal solution. In order to solve for a suboptimal solution, let us resort to the \ac{BCDM} by fixing a block of variables and optimize for others. Since \ac{BCDM} is an iterative method, let us initialize the variable \me{\my} as \me{\iterate{\myb}{0} \in \mc{F}}. Now the problem in \eqref{con} is still nonconvex due to the constraint \eqref{con-dc}, which is in \ac{DC} form. Following the approaches presented in \cite{lipp2014variations,lanckriet2009convergence}, the function \me{g_0(\mx,\iterate{\myb}{0})} is majorized around a feasible point \me{\mxb_0 \in \mc{F}} as

@@

Using the relaxation \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{BCDM} iterate of \me{\myb} and the \me{\ith{k}} linear approximation of \me{\mxb} as

@@

Let the set defined by the problem in \eqref{con-relax} be represented as \me{\iterate{\mc{F}}{i}_k}. In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\iterate{\myb}{i}} and \me{\mx_k}, let us assume that \eqref{con-m} yields \me{\mx_{k+1}} and \me{\mz_{k+1}} as the solution at the \me{\ith{k}} iteration. To show that \me{\mx_{k+1}} and \me{\mz_{k+1}} minimizes the objective function ans also feasible, let us assume that the point \me{\mx_k} is feasible for \eqref{con-m}. Since the function \me{{g}_0(\mx,\iterate{\myb}{i})} is linearized around \me{\mx_k}, it satisfies

@@

since \me{{g}_0(\mx,\iterate{\myb}{i}) \leq \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k), \forall \mx \in \iterate{\mc{F}}{i}_{k-1}}, where \me{\mc{F}_0 = \mc{F}}. Now, \me{\mx_{k+1}} is the solution and feasible for the \me{\ith{k}} subproblem, therefore, it satisfies

@@

Using \eqref{con-sub-set}, we can prove that the solution \me{\mx_{k+1}} and \me{\mz_{k+1}} are feasible, since the initial point \me{\mx_{0}} was chosen to be feasible. In order to prove the convergence of the objective, using \eqref{con-sub-set}, we can see that \me{\iterate{\mc{F}}{i}_{0} \subseteq \dotsc \subseteq \iterate{\mc{F}}{i}_{k-1} \subseteq \iterate{\mc{F}_k}{i} \subseteq \mc{F}}. Since at \me{\ith{k}} iteration, the feasible set of the problem \eqref{con-m} includes the feasible sets of the earlier iteration, we can see that 

@@

f(\mz_0) \geq f(\mz_k) \geq f(\mz_{k+1}) \geq f(\mz_{\ast,y,i}). 

@@

Thus the sequence \me{f(\mz_k)} is nonincreasing and converges to a critical point. Let \me{\mx_{\ast}} and \me{\mz_{\ast,y,i}} be the optimal point of the problem \eqref{con-m} when the iterative algorithm is converged. The symbol \me{y,i} in \me{\mz_{\ast,y,i}} denotes the optimal \me{\mz} with fixed \me{\my} at the \eqn{\ith{i}} \ac{BCDM} iteration. It can be seen from \cite{marks1978technical} that the optimal point of the converged subproblems is in deed the stationary point of the original nonconvex problem \eqref{con}. It can be easily verified by the \ac{KKT} expressions and the feasibility of the constraints.

Once the optimal solution is found for the fixed \me{\my}, we fix the variable \me{\mx} as \me{\iterate{\mxb}{i} = \mx_{\ast}} and optimize \me{\my}. The problem is still nonconvex due to the \ac{DC} constraint. By following similar approach as we discussed for the variable \me{\mx}, we can obtain the optimal solution \me{\my_{k}} for the convex subproblem at the \me{\ith{k}} iteration. The convergence and the nonincreasing behavior of the problem follows similar explanations. Now, the optimal solution of the converged subproblem with \me{\my} as variable is \me{\my_{\ast}} and \me{\mz_{\ast,x,i}}. Following the arguments presented in \cite{marks1978technical}, the optimal point of the converged convex subproblems is a stationary point of the nonconvex problem in \eqref{con}.

Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{BCDM} update, \textit{i.e}, \me{f_0(\mz_{\ast,y,i}) \geq f_0(\mz_{\ast,x,i}) \geq f_0(\mz_{\ast,y,i+1})}. Let us assume that for an initial feasible value of \eqn{\my} at \eqn{\iterate{\my}{0}}, we achieve a stationary point of \eqref{con} by solving sequence of convex subproblems. The solution is given by \eqn{\mz_{\ast,y,0}} and \eqn{\mx_{\ast}}. Now, by fixing \eqn{\iterate{\mx}{0} = \mx_{\ast}}, we find the optimal solution \eqn{\mz_{\ast,x,0}} and \eqn{\my_{\ast}} by solving the convex subproblems. It can be seen that 
\begin{equation}
f_0(\mz_{k,y,0}) \geq f_0(\mz_{\ast,y,0}) \geq f_0(\mz_{0,x,0}) \geq f_0(\mz_{\ast,x,0}),
\end{equation}
which follows from the convexity of the objective function \eqn{f_0} and the initial \eqn{\iterate{\my}{0}} is also a feasible point for the variable \eqn{\my} of the \eqn{\ith{k}} subproblem. Using the property of induction, we can show that the global problem converges to a stationary point of the nonconvex problem \eqref{con} in a nonincreasing manner.

Note that the uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of the proof. We can prove the uniqueness of the convex subproblems defined by \eqref{eqn-9} and \eqref{eqn-mse-2} using the following constraints. For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders is guaranteed by the constraint \eqref{eqn-8}, which can be written as
\begin{equation}
\gamma_{l,k,n} - \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
\end{equation}
where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the convex subproblem \eqref{eqn-mse-2}, uniqueness of the transmit precoder is guaranteed by the constraint 
\begin{multline}
| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \\ + \enoise \leq \epsilon_{l,k,n}.
\end{multline}
Using these arguments, we can claim that the proposed \ac{JSFRA} centralized solution achieves a stationary point of the original nonconvex problem with the nonincreasing objective value at each iteration.

>>>>

\subsubsection{Centralized Problem}

Let us express the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{rCl} \label{con}
\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj} \\
\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
\end{IEEEeqnarray}
wher \me{g_2,f} are convex functions and \me{h} is a linear function. Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both. Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} corresponds to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}. Other convex constraints are addressed by the constraint \eqref{con-cvx}. With this, the feasible set of the problem \eqref{con} is given by 
\begin{IEEEeqnarray}{rl}
\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \nonumber
\end{IEEEeqnarray}

Before proceeding further, let us define the following notations. Let \me{\iterate{\mx}{k}} denote the \me{\ith{k}} \ac{AO} operating point and \me{\mx_k} represent the \me{\ith{k}} \ac{SCA} approximation point. Since the problem \eqref{con} is nonconvex, it is not guaranteed to find the optimal solution. In order to solve for a suboptimal solution, let us resort to the \ac{AO} by fixing a block of variables and optimize for others. Since \ac{AO} is an iterative method, let us initialize the variable \me{\my} as \me{\iterate{\myb}{0} \in \mc{F}}. Now the problem in \eqref{con} is still nonconvex due to the constraint \eqref{con-dc}, which is in \ac{DC} form. Following the approaches presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1}, the function \me{g_0(\mx,\iterate{\myb}{0})} is majorized around a feasible point \me{\mxb_0 \in \mc{F}} by

@@

Using the relaxation \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iterate of \me{\myb} and the \me{\ith{k}} linear approximation of \me{\mxb} as

@@

Let the set defined by the problem in \eqref{con-relax} be represented as \me{\iterate{\mc{X}}{i}_{k} \subset \mc{F}}, where \me{\mc{X}} denotes the subset in which \me{\my} is fixed. In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\iterate{\myb}{i}} and \me{\mx_k}, let us assume that \eqref{con-m} yields \me{\mx_{k+1}} and \me{\mz_{k+1}} as the solution at the \me{\ith{k}} iteration. To show that \me{\mx_{k+1}} and \me{\mz_{k+1}} minimizes the objective function ans also feasible, let us assume that the point \me{\mx_k} is feasible for \eqref{con-m}. Since the function \me{{g}_0(\mx,\iterate{\myb}{i})} is linearized around \me{\mx_k}, it satisfies

@@

since \me{{g}_0(\mx,\iterate{\myb}{i}) \leq \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k), \forall \mx \in \iterate{\mc{X}}{i}_{k-1}}. Now, \me{\mx_{k+1}} is the solution and feasible for the \me{\ith{k}} subproblem, therefore, it satisfies

@@

Using \eqref{con-sub-set}, we can prove that the solution \me{\mx_{k+1}} and \me{\mz_{k+1}} are feasible, since the initial point \me{\mx_{0}} was chosen to be feasible. In order to prove the convergence of the objective, using \eqref{con-sub-set}, we can see that \me{\iterate{\mc{X}}{i}_{0} \subseteq \dots \subseteq \iterate{\mc{X}}{i}_{k-1} \subseteq \iterate{\mc{X}_k}{i} \subset \mc{F}}. Since at \me{\ith{k}} iteration, the feasible set of the problem \eqref{con-m} includes the feasible sets of the earlier iteration, we can see that 

@@

f(\mz_0) \geq f(\mz_k) \geq f(\mz_{k+1}) \geq f(\mz_{\ast,x,i}). 

@@

Thus the sequence \me{f(\mz_k)} is nonincreasing and converges to a critical point. Let \me{\mx_{\ast}} and \me{\mz_{\ast,x,i}} be the optimal point of the problem \eqref{con-m} when the iterative algorithm is converged. The symbol \me{x,i} in \me{\mz_{\ast,x,i}} denotes the optimal \me{\mz} is found over the variable \me{\mx} at the \eqn{\ith{i}} \ac{AO} iteration. Note that this point need not be the stationary point of the original nonconvex problem \eqref{con} since it minimizes over the feasible set \me{\iterate{\mc{X}_{\ast}}{i} \subseteq \iterate{\mc{X}_{\ast}}{i+1} \subset \mc{F}}, which depend on the variable \me{\mx} only. The optimal point \me{\mz_{\ast,x,i}} of the convex subproblem \eqref{con-m} is a stationary point of the nonconvex problem \eqref{con} only over the set \me{\iterate{\mc{X}_{\ast}}{i}}.

Once the optimal solution is found for the fixed \me{\my}, we fix the variable \me{\mx} as \me{\iterate{\mxb}{i} = \mx_{\ast}} and optimize \me{\my}. The problem is still nonconvex due to the \ac{DC} constraint. By following similar approach as earlier, we can obtain an optimal solution \me{\my_{k}} for the convex subproblem at the \me{\ith{k}} iteration. The convergence and the nonincreasing behavior of the problem follows similar explanations. Now, the optimal solution of the converged subproblem with \me{\my} as variable is \me{\my_{\ast}} and \me{\mz_{\ast,y,i}}. Note that the solution \me{\mz_{\ast,y,i}} is the minimizer for the subset \me{\iterate{\mc{Y}_{\ast}}{i}}

Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, \me{f_0(\mz_{\ast,x,i}) \geq f_0(\mz_{\ast,y,i}) \geq f_0(\mz_{\ast,x,i+1})}. Let us assume that for an initial feasible value of \eqn{\my} at \eqn{\iterate{\my}{0}}, we achieve a feasible point of \eqref{con} by solving sequence of convex subproblems. The solution is given by \eqn{\mz_{\ast,x,0}} and \eqn{\mx_{\ast}}. Now, by fixing \eqn{\iterate{\mx}{0} = \mx_{\ast}}, we find next feasible solution \eqn{\mz_{\ast,y,0}} and \eqn{\my_{\ast}} for \eqref{con} by solving the convex subproblems \eqref{con-m}. It can be seen that 
\begin{equation}
f_0(\mz_{k,x,0}) \geq f_0(\mz_{\ast,x,0}) \geq f_0(\mz_{0,y,0}) \geq f_0(\mz_{\ast,y,0}),
\end{equation}
which follows from the convexity of the objective function \eqn{f_0} and the initial \eqn{\iterate{\my}{0}} is also a feasible point for the variable \eqn{\my} at the \eqn{\ith{k}} subproblem, \textit{i.e}, 
\begin{equation}
\iterate{\mc{X}}{i}_{0} \dots \subseteq \iterate{\mc{X}}{i}_{\ast} \subseteq \iterate{\mc{Y}_{0}}{i} \dots \subseteq \iterate{\mc{Y}}{i}_{\ast} \subseteq \mc{F}.
\end{equation}
Using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner.

To show the converged point of the iterative algorithm is in fact the stationary point of the nonconvex problem \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem. Since the converged point is the minimizer for the iterative algorithm such that 
\begin{equation} \label{con-opt}
f_0(\mz_{\ast,x,i}) = f_0(\mz_{\ast,y,i}) = f_0(\mz_{\ast,x,i+1}),
\end{equation}
the solution is inside the feasible set \me{\mc{F}} and \me{\mz_{\ast,x,i+1}} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}, which includes all optimal points of \me{\mz} identified so far. Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mz_{\ast,x,i+1}} is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions.

Note that the uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of \ac{AO}. We can prove the uniqueness of the convex subproblems defined by \eqref{eqn-9} and \eqref{eqn-mse-2} using the following constraints. For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders is guaranteed by the constraint \eqref{eqn-8}, which can be written as
\begin{multline}
\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
\end{multline}
where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the convex subproblem \eqref{eqn-mse-2}, uniqueness of the transmit precoder is guaranteed by the constraint 
\begin{multline}
| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
\end{multline}
Using these arguments, we can claim that the proposed \ac{JSFRA} centralized solution achieves a stationary point of the original nonconvex problem with the nonincreasing objective value at each iteration.

### 2015-01-23 Report/kkt_mse_approach.tex
changes with satya
manosha

In this section, we discuss different ways to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}. In contrast to Section \ref{sec-4a}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations. The proposed methods in this section provide algorithms that can be of practical importance due to the limited signaling requirements. Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}. Since the formulation in \cite{kaleva2013decentralized,kaleva2013primal} are similar to the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, it requires explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.

@@

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \eqspace \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
	\text{subject to} & \nonumber \\
	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \|\mvec{w}{l,k,n}\|^2 \nonumber \\
	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.

>>>>

In this section, we discuss an alternative way to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}. In contrast to Section \ref{sec-4a}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations. The proposed methods in this section provide algorithms that can be of practical importance \review{in the \ac{TDD} system} due to the limited signaling requirements. Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}. Since the formulation in \cite{kaleva2013decentralized,kaleva2013primal} are similar to the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, it requires explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.

@@

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \eqspace \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
	\text{subject to} & \nonumber \\
	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise \nonumber \\
	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.
